\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage[margin=1in]{geometry}

\newcommand{\NoisyFlow}{NoisyFlow}

\title{Hard Synthetic Mixture-of-Gaussians Benchmark (Ref-100)}
\author{}
\date{}

\begin{document}
\maketitle

\section{Dataset construction}
We consider a federated mixture-of-Gaussians classification benchmark (\texttt{federated\_mixture\_gaussians}).
Let $C$ denote the number of classes and $d$ the feature dimension.
We sample class means $\{\mu_c\}_{c=1}^C$ with $\mu_c \sim \mathcal{N}(0,\alpha^2 I)$ and generate labeled base samples by drawing $y \sim \mathrm{Unif}(\{1,\dots,C\})$ and $x_0 \sim \mathcal{N}(\mu_y,\beta^2 I)$.
Federated heterogeneity is induced by applying an independent random affine map per client, $x = A_k x_0 + b_k$, yielding $K$ source domains.
We generate the target domain by applying a separate affine map $x = A_t x_0 + b_t$ and split it into a target-reference set and a target-test set.

\paragraph{Parameters.}
We set $K=3$, $n_{\text{per\_client}}=1500$, $n_{\text{target\_ref}}=2000$, $n_{\text{target\_test}}=1000$, $d=50$, $C=6$, $\alpha=0.45$ (\texttt{component\_scale}), $\beta=1.15$ (\texttt{component\_cov}), and seed $=0$.

\section{Results (seed=0)}
We evaluate classification accuracy on the target-test split.
We train RandomForest classifiers on (i) \textbf{Ref-only:} $n_{\text{ref}}=100$ labeled target-reference examples, (ii) \textbf{Synth-only:} transported synthetic target-like examples, and (iii) \textbf{Ref+Synth:} the union of the two training sets.
We generate $K \cdot M_{\text{per\_client}} = 3 \cdot 5000 = 15{,}000$ labeled transported synthetic samples.
Table~\ref{tab:mog-ref100} shows that augmenting the labeled target-reference set with transported synthetic samples improves accuracy by 6.8 points over the ref-only baseline.

\begin{table}[t]
  \centering
  \begin{tabular}{lccccc}
    \toprule
    Setting &
    Train $n$ &
    Test $n$ &
    Acc &
    $\Delta$ (vs Ref-only) \\
    \midrule
    Ref-only ($n_{\text{ref}}=100$) & 100 & 1000 & 0.602 & --- \\
    Synth-only ($K\cdot M_{\text{per\_client}}$) & 15000 & 1000 & 0.671 & +0.069 \\
    Ref+Synth & 15100 & 1000 & 0.670 & +0.068 \\
    \bottomrule
  \end{tabular}
  \caption{Synthetic mixture-of-Gaussians benchmark (single run, seed=0). $\Delta=\text{Acc}-\text{Acc(Ref-only)}$.}
  \label{tab:mog-ref100}
\end{table}

\end{document}
